### 2016-11-10 thesis/intro/intro.tex
tmp commit

\gls{pomc} is a precursor protein that is cleaved to produce \gls{acth}, $\alpha$-, $\beta$- and $\gamma$-\gls{msh}, and $\beta$-endorphin (citation Smith1988, endocr. rev.).
Perhaps the most important, or most relevant, in the context of obesity and satiety control is the $\alpha$-MSH.
$\alpha$-MSH is the main ligand that binds to the \gls{mc4r} expressed in the brain, and sends anorexogenic signals to the downstream neurons through this pathway \citep{Krude1998}.

Similarly, \gls{cart} is also a neuropeptide that has a strong anorexogenic effect discovered by (citation Kristensen1998 on CART).
Unlike $\alpha$-MSH, the receptor for \gls{cart} has not been identified yet, and the exact mechanism in which \gls{cart} acts is unclear (citation... Kristensen1998, Rogge2008).

@@

\gls{npy} was first discovered by \citet{Tatemoto1982}, and later associated with altered eating behaviour in rats by \citet{Clark1984}.
\gls{npy} is recognised by the \gls{nyr}, a G protein-coupled receptor expressed on the downstream effector neurons, which relays the orexogenic signal from the \gls{npy}/\gls{agrp} neurons (citation, Herzog 1992 PNAS) \citep{Barsh2002, Bell2005}

@@

\noindent
Ghrelin, originally identified as a peptide that stimulated the release of growth hormone from the pituitary, is a hormone produced mainly in the stomach that has a significant role in meal initiation and food intake, as well as energy homeostasis \citep{Kohno2003} (citation, nakazato2001 nature, kojima1999 nature).
Ghrelin is known to be a ligand for the \gls{ghsr} which is expressed abundantly on the \gls{npy}/\gls{agrp} neurons, and increases the Ca$^{2+}$ concentration in these neurons \citep{Kohno2003}.

Furthermore, (citation Seaone2003) showed that ghrelin increased the mRNA levels of both \gls{npy} and \gls{agrp} in these neurons and hence their protein expression, indicating the role of ghrelin as the orexogenic hormone that affects the overall outcome of the satiety signal.
\\

\noindent
Leptin, on the otherhand, is a hormone that has an opposite effect as ghrelin, where the hormone signals satiety and reduces food intake.
First identified by \citet{Zhang1994}, the dicovery of the leptin gene, followed by the discovery of leptin receptor gene by \citet{Tartaglia1995}, were probably the major breakthrough in the field of obesity research.
\\

\noindent
Insulin, perhaps the most well-known hormone for its role in glucose homeostasis, also has an important role in satiety and food intake regulation.
\\

>>>>

\gls{pomc} is a precursor protein that is cleaved to produce \gls{acth}, $\alpha$-, $\beta$- and $\gamma$-\gls{msh}, and $\beta$-endorphin \citep{Smith1988}.
Perhaps the most important, or most relevant, in the context of obesity and satiety control is the $\alpha$-MSH.
$\alpha$-MSH is the main ligand that binds to the \gls{mc4r} expressed in the brain, and sends anorexogenic signals to the downstream neurons through this pathway \citep{Krude1998}.

Similarly, \gls{cart} is also a neuropeptide that has a strong anorexogenic effect discovered by \citet{Kristensen1998}.
Unlike $\alpha$-MSH, the receptor for \gls{cart} has not been identified yet, and the exact mechanism in which \gls{cart} acts is unclear \citep{Kristensen1998, Rogge2008}.

@@

\gls{npy} was first discovered by \citet{Tatemoto1982}, and later associated with altered eating behaviour in rats by \citet{Clark1984}.
\gls{npy} is recognised by the \gls{nyr}, a G protein-coupled receptor expressed on the downstream effector neurons, which relays the orexogenic signal from the \gls{npy}/\gls{agrp} neurons \citep{Barsh2002, Bell2005, Herzog1992}

@@

\noindent
Ghrelin, originally identified as a peptide that stimulated the release of growth hormone from the pituitary, is a hormone produced mainly in the stomach that has a significant role in meal initiation and food intake, as well as energy homeostasis \citep{Kohno2003, Kojima1999, Nakazato2001}.
Ghrelin is known to be a ligand for the \gls{ghsr} which is expressed abundantly on the \gls{npy}/\gls{agrp} neurons, and increases the Ca$^{2+}$ concentration in these neurons \citep{Kohno2003}.

Furthermore, \citet{Seoane2003} showed that ghrelin increased the mRNA levels of both \gls{npy} and \gls{agrp} in these neurons and hence their protein expression, indicating the role of ghrelin as the orexogenic hormone that affects the overall outcome of the satiety signal.
\\

\noindent
Leptin, on the other hand, is a hormone that has an opposite effect as ghrelin, where the hormone signals satiety and reduces food intake.
First identified by \citet{Zhang1994}, the dicovery of the leptin gene, followed by the discovery of leptin receptor gene by \citet{Tartaglia1995}, were probably the major breakthrough in the field of obesity research.

Leptin is produced and secreted mainly by the white adipose tissue, and the circulating concentration of leptin in the body is proportional to body fat stores \citep{Barsh2002, Moustafa2013, Zhang1994}.
Leptin receptor has many splice variants, but the long variant of the leptin receptor is highly expressed only in the hypothalamus \citep{Ghilardi1996, Lee1996}.
In addition to this, leptin receptor is expressed on both the \gls{npy}/\gls{agrp} and \gls{pomc}/\gls{cart} neurons, and have different effect on the outcome of the satiety signal depending on which neuron leptin stimulates.

In \gls{npy}/\gls{agrp} neuron, it has been shown to reduce the Ca$^{2+}$ concentration, antagonising the effect of ghrelin on this type of neurons \citep{Kohno2003}.
Furthermore, binding of leptin to the leptin receptor on the \gls{npy}/\gls{agrp} neuron causes a decreased release of \gls{gaba}, which inhibits the \gls{pomc}/\gls{cart} neuron \citep{Cowley2001}.

In \gls{pomc}/\gls{cart} neuron, binding of leptin to its recpetor causes a depolarisation of the neuron \citep{Cowley2001}.
Together with the indirect effect from the \gls{npy}/\gls{agrp} neuron, leptin inhibits the \gls{pomc}/\gls{cart} neuron to release $\alpha$-\gls{msh}, and therefore sends a satiety signal to its downstream effector neurons.
\\

\noindent
Insulin, perhaps the most well-known hormone for its role in glucose homeostasis, also has an important role in satiety and food intake regulation.

Briefly, when insulin binds to the insulin receptor, \gls{irs} protein family is recruited and phosphorylated by the insulin receptor's intrinsic tyrosine kinase activity \citep{Saltiel2002}.
The phosphorylated \gls{irs} protein then activates \gls{pi3k}, which in turn activates its downstream targets, causing a rapid signal cascade through the cell \citep{Saltiel2002}.

It was first noticed by \citet{Spanswick1997} that insulin showed a very similar 
\\
